Data Prep: IUCN and AquaMaps

### 2016-12-27 data_explore/data_explore.Rmd
pushing recent updates to analysis and documentation based on reviewer comments

data_file <- file.path(dir_data, 'spp_list_w_area_trimmed.csv')
spp_map_pairs <- read.csv(data_file, stringsAsFactors = FALSE) %>%
  filter(!is.na(popn_category)) %>% ### filter out unassessed species
  filter(!is.na(sm_perc))           ### filter out NA maps

@@

spp_gp_quadrants <- spp_gp_quadrants %>%
  left_join(spp_gp_quadrants %>% 
              filter(quad == 'q1') %>%
              dplyr::select(spp_group_text, pct_q1 = pct_quad),
            by = 'spp_group_text') %>%
  left_join(quad_names, by = 'quad')

@@

### Plot the bar chart
barchart_spp_gp_quads <- ggplot(spp_gp_quadrants %>% 
                                  transform(spp_group_text = reorder(spp_group_text, pct_q1)), 
                                aes(x = spp_group_text, fill = quad, weight = pct_quad)) +
  ggtheme_plot + 
  theme(panel.grid.major.y = element_blank()) +
  geom_bar(stat = 'count', alpha = 1) +
  scale_fill_manual(values = c('q4' = '#d01c8b', 
                               'q3' = '#f1b6da', 
                               'q2' = '#b8e186',
                               'q1' = '#4dac26'),
                    labels = quad_names$quad_name) +
  scale_y_continuous(expand = c(0, 0), 
                     limits = c(0, 1.1),
                     breaks = break_nums/100,
                     labels = sprintf('%s%%', break_nums)) + 
  ### add grid lines; horizontal but then get flipped
  geom_hline(yintercept = break_nums/100, size = 0.25, color = 'white', alpha = .5) +
  ### add text
  geom_text(# data = spp_gp_quadrants %>%
              # select(spp_group_text, n_spp) %>%
              # distinct(),
            aes(label = sprintf('n = %s', n_spp), y = 1.01), hjust = 0, 
            size = 2.5, 
            color = 'grey30') +
  coord_flip() +
  labs(x = 'Taxonomic Group', 
       y = 'Percent of species by quadrant', 
       fill = 'Alignment')

@@

# ggsave(plot = barchart_spp_gp_quads,
#        filename = file.path(dir_fig, 'barchart_spp_gp_quads.png'),
#        width = 19.05, height = 7, units = 'cm', dpi = 600)

@@

>>>>

data_file <- file.path(dir_data, 'spp_list_w_area_trimmed.csv')
spp_map_pairs <- read_csv(data_file)

@@

spp_gp_quadrants <- spp_gp_quadrants %>%
  left_join(spp_gp_quadrants %>% 
              filter(quad == 'q1') %>%
              dplyr::select(spp_group_text, pct_q1 = pct_quad),
            by = 'spp_group_text') %>%
  left_join(quad_names, by = 'quad') %>% 
  mutate(quad = factor(quad, levels = c('q4', 'q3', 'q2', 'q1'))) %>%
  transform(spp_group_text = reorder(spp_group_text, pct_q1))

@@

### Plot the bar chart
barchart_spp_gp_quads <- ggplot(spp_gp_quadrants, 
                                aes(x = spp_group_text, fill = quad, weight = pct_quad)) +
  ggtheme_plot + 
  # theme(panel.grid.major.y = element_blank()) +
  geom_bar(stat = 'count', alpha = 1) +
  scale_fill_manual(values = c('q1' = '#4dac26', 
                               'q2' = '#b8e186', 
                               'q3' = '#f1b6da',
                               'q4' = '#d01c8b'),
                    labels = quad_names$quad_name) +
  scale_y_continuous(expand = c(0, 0), 
                     limits = c(0, 1.1),
                     breaks = break_nums/100,
                     labels = sprintf('%s%%', break_nums)) + 
  ### add grid lines; horizontal but then get flipped
  geom_hline(yintercept = break_nums/100, size = 0.25, color = 'white', alpha = .5) +
  ### add text
  geom_text(# data = spp_gp_quadrants %>%
              # select(spp_group_text, n_spp) %>%
              # distinct(),
            aes(label = sprintf('n = %s', n_spp), y = 1.01), hjust = 0, 
            size = 2.5, 
            color = 'grey30') +
  coord_flip() +
  labs(x = 'Taxonomic Group', 
       y = 'Percent of species by quadrant', 
       fill = 'Alignment')

@@

# ggsave(plot = barchart_spp_gp_quads,
       filename = file.path(dir_fig, 'barchart_spp_gp_quads.png'),
       width = 19.05, height = 7, units = 'cm', dpi = 600)

@@

## quad plot experts only

spp_list_experts <- spp_list %>%
  filter(reviewed == 1)

### means for both x and y axes - use original means
area_align_mean <- mean(spp_list$area_ratio, na.rm = TRUE)
dist_align_mean <- mean(spp_list$sm_perc, na.rm = TRUE)

area_align_mean_ex <- mean(spp_list_experts$area_ratio, na.rm = TRUE)
dist_align_mean_ex <- mean(spp_list_experts$sm_perc, na.rm = TRUE)

spp_list_experts_labs <- spp_list_experts %>%
  rename(x = area_ratio, y = sm_perc) %>%
  mutate(fade = FALSE,
         fade = ifelse((x > q1[1] & x < q1[2] & y > q1[3] & y < q1[4]), TRUE, fade),
         fade = ifelse((x > q2[1] & x < q2[2] & y > q2[3] & y < q2[4]), TRUE, fade),
         fade = ifelse((x > q3[1] & x < q3[2] & y > q3[3] & y < q3[4]), TRUE, fade),
         fade = ifelse((x > q4[1] & x < q4[2] & y > q4[3] & y < q4[4]), TRUE, fade))

### mongo plot time
scatter_quadplot_ex <- ggplot(spp_list_experts_labs, aes(x = x, y = y)) +
  ggtheme_plot + 
  ### color the quadrant backgrounds:
  annotate("rect", xmin = area_align_mean, xmax = 100, ymin = dist_align_mean, ymax = 100, 
           alpha = .3, fill= "#4dac26")  + 
  annotate("rect", xmax = area_align_mean, xmin =   0, ymin = dist_align_mean, ymax = 100, 
           alpha = .3, fill= "#b8e186") + 
  annotate("rect", xmin = area_align_mean, xmax = 100, ymax = dist_align_mean, ymin =   0, 
           alpha = .3, fill= "#f1b6da") + 
  annotate("rect", xmax = area_align_mean, xmin =   0, ymax = dist_align_mean, ymin =   0, 
           alpha = .3, fill= "#d01c8b") +
  ### add grid lines
  geom_vline(xintercept = break_nums, size = 0.25, color = 'white', alpha = .5) +
  geom_hline(yintercept = break_nums, size = 0.25, color = 'white', alpha = .5)

### plot the data points!
scatter_quadplot_ex <- scatter_quadplot_ex +
  # geom_point(color = '#4d4dac', aes(alpha = fade), show.legend = FALSE) +
  # geom_point(data = spp_list_experts_labs %>%
  #              filter(str_detect(spp_group_text, 'Corals')),
  #            color = 'red', aes(alpha = fade), 
  #            shape = 4, stroke = .5, 
  #            size = 1, show.legend = FALSE) +
  # scale_alpha_manual(values = c('TRUE' = .15, 'FALSE' = 1)) +
  geom_point(color = 'black', aes(alpha = fade), size = .1, show.legend = FALSE) +
  scale_alpha_manual(values = c('TRUE' = .15, 'FALSE' = 1))

### label the quadrants:
scatter_quadplot_ex <- scatter_quadplot_ex +
  annotate("text", x = 97, y = 95, hjust = 1, vjust = .5, size = 3, color = 'grey20', 
           fontface = 'bold.italic', label = "Well-aligned") + 
  annotate("text", x =  3, y = 95, hjust = 0, vjust = .5, size = 3, color = 'grey20',
           fontface = 'bold.italic', label = "Distribution-aligned") + 
  annotate("text", x = 97, y =  5, hjust = 1, vjust = .5, size = 3, color = 'grey20',
           fontface = 'bold.italic', label = "Area-aligned") + 
  annotate("text", x =  3, y =  5, hjust = 0, vjust = .5, size = 3, color = 'grey20',
           fontface = 'bold.italic', label = "Poorly aligned")

### Manage axis scales 
scatter_quadplot_ex <- scatter_quadplot_ex +
  scale_x_continuous(expand = c(0, 0), limits = c(-1, 101),
                     breaks = break_nums,
                     labels = sprintf('%s%%', break_nums)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(-1, 101),
                     breaks = break_nums,
                     labels = sprintf('%s%%', break_nums))

### here are mean labels:
scatter_quadplot_ex <- scatter_quadplot_ex +
  annotate(geom = 'text', x = area_align_mean, y = 5,
           hjust = 0, vjust = 0, color = 'grey30', size = 2,
           fontface = 'bold.italic', angle = 90,
           label = sprintf('Mean (all) = %s%%', round(area_align_mean, 1))) +
  annotate(geom = 'text', x = 5, y = dist_align_mean,
           hjust = 0, vjust = 0, color = 'grey30', size = 2,
           fontface = 'bold.italic', angle = 0,
           label = sprintf('Mean (all) = %s%%', round(dist_align_mean, 1))) +
  geom_hline(yintercept = dist_align_mean_ex, color = 'grey40', linetype = 2, size = 0.25) + 
  geom_vline(xintercept = area_align_mean_ex, color = 'grey40', linetype = 2, size = 0.25) + 
  annotate(geom = 'text', x = area_align_mean_ex - .25, y = 5,
           hjust = 0, vjust = 0, color = 'grey30', size = 2,
           fontface = 'bold.italic', angle = 90,
           label = sprintf('Mean (reviewed) = %s%%', round(area_align_mean_ex, 1))) +
  annotate(geom = 'text', x = 5, y = dist_align_mean_ex + .25,
           hjust = 0, vjust = 0, color = 'grey30', size = 2,
           fontface = 'bold.italic', angle = 0,
           label = sprintf('Mean (reviewed) = %s%%', round(dist_align_mean_ex, 1)))

scatter_quadplot_ex <- scatter_quadplot_ex +
  labs(x = bquote('Area ratio '*alpha['ext']*' (%)'), 
       y = bquote('Distribution alignment '*alpha['dist']*' (%)'))

# print(scatter_quadplot_ex)

# ggsave(file.path(dir_fig, 'scatter_quadmap_expert.png'),
#        width = 19.05, height = 9, units = 'cm', dpi = 600)

## Break down quads by species group for expert reviewed maps

### means for both x and y axes - use original means
area_align_mean <- mean(spp_list$area_ratio, na.rm = TRUE)
dist_align_mean <- mean(spp_list$sm_perc, na.rm = TRUE)

spp_list_experts1 <- spp_list_experts %>%
  group_by(spp_group_text) %>%
  mutate(n_spp = n()) %>%
  ungroup()

### Create species lists by quadrant
spp_list_experts_q1 <- spp_list_experts1 %>%
  filter(area_ratio >= area_align_mean & sm_perc >= dist_align_mean)
spp_list_experts_q2 <- spp_list_experts1 %>%
  filter(area_ratio <  area_align_mean & sm_perc >= dist_align_mean)
spp_list_experts_q3 <- spp_list_experts1 %>%
  filter(area_ratio >= area_align_mean & sm_perc < dist_align_mean)
spp_list_experts_q4 <- spp_list_experts1 %>%
  filter(area_ratio <  area_align_mean & sm_perc < dist_align_mean)

spp_list_experts_quads <- spp_list_experts1 %>%
  mutate(quad = NA,
         quad = ifelse(is.na(quad) & sciname %in% spp_list_experts_q1$sciname, 'q1', quad),
         quad = ifelse(is.na(quad) & sciname %in% spp_list_experts_q2$sciname, 'q2', quad),
         quad = ifelse(is.na(quad) & sciname %in% spp_list_experts_q3$sciname, 'q3', quad),
         quad = ifelse(is.na(quad) & sciname %in% spp_list_experts_q4$sciname, 'q4', quad))
write_csv(spp_list_experts_quads, file.path(dir_data, 'spp_list_experts_quads.csv'))

### Summarize quadrant species list by species group (e.g. CORALS1)
spp_gp_q1_ex <- spp_list_experts_q1 %>%
  group_by(spp_group_text) %>%
  summarize(n_spp = first(n_spp), n_spp_q1 = n())
spp_gp_q2_ex <- spp_list_experts_q2 %>%
  group_by(spp_group_text) %>%
  summarize(n_spp = first(n_spp), n_spp_q2 = n())
spp_gp_q3_ex <- spp_list_experts_q3 %>%
  group_by(spp_group_text) %>%
  summarize(n_spp = first(n_spp), n_spp_q3 = n())
spp_gp_q4_ex <- spp_list_experts_q4 %>%
  group_by(spp_group_text) %>%
  summarize(n_spp = first(n_spp), n_spp_q4 = n())

### Join species group by quadrant into a single dataframe
spp_gp_quads_ex <- spp_gp_q1_ex %>%
  full_join(spp_gp_q2_ex, by = c('spp_group_text', 'n_spp')) %>%
  full_join(spp_gp_q3_ex, by = c('spp_group_text', 'n_spp')) %>%
  full_join(spp_gp_q4_ex, by = c('spp_group_text', 'n_spp')) %>%
  gather(quad, n_quad, n_spp_q1, n_spp_q2, n_spp_q3, n_spp_q4) %>% 
  mutate(quad = str_replace(quad, 'n_spp_', ''),
         pct_quad = n_quad/n_spp,
         n_quad   = ifelse(is.na(n_quad),   0, n_quad),
         pct_quad = ifelse(is.na(pct_quad), 0, pct_quad))

spp_gp_quads_ex <- spp_gp_quads_ex %>%
  left_join(spp_gp_quads_ex %>% 
              filter(quad == 'q1') %>%
              dplyr::select(spp_group_text, pct_q1 = pct_quad),
            by = 'spp_group_text') %>%
  left_join(quad_names, by = 'quad') %>% 
  mutate(quad = factor(quad, levels = c('q4', 'q3', 'q2', 'q1'))) %>%
  transform(spp_group_text = reorder(spp_group_text, pct_q1))

### Plot the bar chart
bar_spp_gp_quads_ex <- ggplot(spp_gp_quads_ex, 
                                aes(x = spp_group_text, fill = quad, weight = pct_quad)) +
  ggtheme_plot + 
  # theme(panel.grid.major.y = element_blank()) +
  geom_bar(stat = 'count', alpha = 1) +
  scale_fill_manual(values = c('q1' = '#4dac26', 
                               'q2' = '#b8e186', 
                               'q3' = '#f1b6da',
                               'q4' = '#d01c8b'),
                    labels = quad_names$quad_name) +
  scale_y_continuous(expand = c(0, 0), 
                     limits = c(0, 1.1),
                     breaks = break_nums/100,
                     labels = sprintf('%s%%', break_nums)) + 
  ### add grid lines; horizontal but then get flipped
  geom_hline(yintercept = break_nums/100, size = 0.25, color = 'white', alpha = .5) +
  ### add text
  geom_text(# data = spp_gp_quadrants %>%
              # select(spp_group_text, n_spp) %>%
              # distinct(),
            aes(label = sprintf('n = %s', n_spp), y = 1.01), hjust = 0, 
            size = 2.5, 
            color = 'grey30') +
  coord_flip() +
  labs(x = 'Taxonomic Group', 
       y = 'Percent of species by quadrant', 
       fill = 'Alignment')

print(bar_spp_gp_quads_ex)

# ggsave(plot = bar_spp_gp_quads_ex,
       filename = file.path(dir_fig, 'barchart_spp_gp_quads_ex.png'),
       width = 19.05, height = 7, units = 'cm', dpi = 600)

write_csv(spp_gp_quadrants, file.path(dir_data, 'spp_gp_quads_ex.csv'))

### 2016-12-27 data_explore/data_explore_am_thresh.Rmd
pushing recent updates to analysis and documentation based on reviewer comments

spp_cells <- read_csv(file.path(dir_aquamaps, 'csv/hcaf_sp_native_trunc.csv'), 
                      col_types = 'ccd', progress = TRUE)

@@

>>>>

spp_cells <- read_csv(file.path(dir_aquamaps, 'csv/hcaf_sp_native_trunc.csv'),
                      progress = TRUE)

@@

``` {r inspect_extrapolation_ratios}
spp_list <- read_csv(file.path(dir_git, 'data/spp_list_w_area_trimmed.csv'))
hcaf <- read_csv(file.path(dir_aquamaps, 'csv/hcaf_truncated.csv'))

spp_cell_matches <- spp_cells %>%
  rename(am_sid = speciesid) %>%
  filter(am_sid %in% spp_list$am_sid | am_sid %in% c('Fis-131802', 'W-Oph-245456')) %>%
  left_join(hcaf, by = 'loiczid') %>%
  mutate(probability = as.numeric(probability)) %>%
  select(-csquarecode, -contains('limit'), -contains('center'))

spp_cell_sums <- spp_cell_matches %>%
  group_by(am_sid) %>%
  summarize(n_cells = n(),
            area    = sum(oceanarea, na.rm = TRUE),
            area_wt = sum(oceanarea * probability, na.rm = TRUE)) %>%
  left_join(spp, by = c('am_sid' = 'speciesid')) %>%
  select(am_sid, n_cells, area, area_wt, sciname, reviewed, occurcells) %>%
  mutate(geog_space_extrapolate = area / occurcells,
         env_space_extrapolate = area_wt / occurcells)

spp_cell_sums_Oplana <- spp_cells %>%
  filter(speciesid == 'W-Oph-245456')
spp_cell_sums_Rfyllae <- spp_cells %>%
  filter(speciesid == 'Fis-131802')

hist(spp_cell_sums_Oplana$probability)
hist(spp_cell_sums_Rfyllae$probability)

summary(spp_cell_sums_Oplana$probability)
summary(spp_cell_sums_Rfyllae$probability)
### Very similar distributions
# > summary(spp_cell_sums_Oplana$probability)
#    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#  0.0100  0.2300  0.6000  0.5725  0.9600  1.0000 
# > summary(spp_cell_sums_Rfyllae$probability)
#    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#  0.0100  0.2300  0.6500  0.5981  1.0000  1.0000

### How do prob-weighted areas compare to non-prob-weighted areas?  consistent 
### ratio would indicate that the uncertainty due to # of occurcells is not
### being considered in the predictions

spp_cell_sums1 <- spp_cell_sums %>%
  mutate(a_to_a_wt = area / area_wt,
         gspace_to_espace = geog_space_extrapolate / env_space_extrapolate) %>%
  arrange(desc(a_to_a_wt)) %>%
  filter(a_to_a_wt < 50) ### get rid of Zalophus wollbaeki outlier

summary(spp_cell_sums1$a_to_a_wt)
  #  Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  # 1.023   1.258   1.371   1.495   1.571   8.062 
summary(spp_cell_sums1$gspace_to_espace)
### haha the same, duh
### but fairly consistent ratios seem to indicate no relationship

summary(lm(a_to_a_wt ~ occurcells, data = spp_cell_sums1))
# Adjusted R-squared:  0.01058 - essentially no explanatory power
```

### 2016-12-27 data_explore/data_prep.Rmd
pushing recent updates to analysis and documentation based on reviewer comments

dir_M <- c('Windows' = '//mazu.nceas.ucsb.edu/data_edit',
           'Darwin'  = '/Volumes/ohi',
           'Linux'   = '/var/data/ohi')[[ Sys.info()[['sysname']] ]]

@@

loiczid_raster_file  <- file.path(dir_git, 'shiny/data/loiczid_raster.grd')
loiczid_raster       <- raster::raster(loiczid_raster_file)
names(loiczid_raster) <- 'loiczid'

@@

  ### species info list - scinames, IUCN species ID, AM species ID, category etc
  spp_list_base <- read_csv(file.path(dir_data, 'spp_am_v_iucn.csv'))

  create_spp_list(spp_list_base, data_file, am_spp_cells, iucn_spp_cells, loiczid_raster)
}

@@

### attach group name text field, and occurcells field
spp_list <- spp_list %>%
  left_join(x <- read_csv(file.path(dir_data, 'sciname_lookups/spp_groupnames.csv')),
            by = 'spp_group') %>%
  left_join(read_csv(file.path(dir_data_remote, 'aquamaps/v2015/csv/speciesoccursum.csv')) %>% 
              select(am_sid = speciesid, occurcells),
            by = 'am_sid')

cat_score_df <- data.frame(popn_category  = c('LC', 'NT', 'VU', 'EN', 'CR', 'EX', 'DD', 'NE'),
                           category_score = c( 0.0,  0.2,  0.4,  0.6,  0.8,  1.0,   NA,  NA))
spp_list <- spp_list %>%
  left_join(cat_score_df, by = 'popn_category')

@@

``` {r counts_spp_all_observations, echo = FALSE}
spp_all <- read_csv(file.path(dir_data, 'spp_all.csv'))

@@

totes_occur <- obis_occur %>%
  left_join(gbif_occur) %>%
  rowwise() %>%
  mutate(mean_occ = mean(c(gbif_occ, obis_occ), na.rm = TRUE))

@@

__Possible "data poor" indicators:__

* (of matched species) how does bottom decile get distributed across quadrants
* use mean of OBIS and GBIF, and just report average (or median?) occurrences across all species in each quadrant
* also use similar method for AM occurcells

``` {r data_poor_analysis, echo = FALSE, eval = FALSE}
spp_quads <- read_csv(file.path(dir_data, 'spp_list_quads.csv')) %>% 
  select(am_sid, iucn_sid, occurcells, quad) %>%
  unique()
### This contains all mapped species, discarding those with no actual IUCN maps

spp_occ_counts <- spp_quads %>%
  left_join(totes_occur) %>%
  group_by(iucn_sid, am_sid, quad) %>%
  summarize(occurcells = mean(occurcells, na.rm = TRUE), occ = mean(mean_occ, na.rm = TRUE)) %>%
  group_by(iucn_sid, quad) %>%
  summarize(occurcells = sum(occurcells, na.rm = TRUE), occ = sum(occ, na.rm = TRUE)) %>%
  ungroup()

btm_dec_occurcells <- spp_occ_counts$occurcells %>% quantile(c(.1, .25))
btm_dec_occ <- spp_occ_counts$occ %>% quantile(c(.1, .25))

quad_count_means <- spp_occ_counts %>%
  mutate(quad = ifelse(quad == 'q4', 'q4', 'q123')) %>%
  group_by(quad) %>%
  summarize(mean_occurcells = mean(occurcells),
            mean_occ        = mean(occ),
            med_occurcells  = median(occurcells),
            med_occ         = median(occ),
            dp_am_10 = sum(occurcells <= btm_dec_occurcells[1])/n(),
            dp_am_25 = sum(occurcells <= btm_dec_occurcells[2])/n(),
            dp_gb_10 = sum(occ <= btm_dec_occ[1])/n(),
            dp_gb_25 = sum(occ <= btm_dec_occ[2])/n())

write_csv(quad_count_means, file.path(dir_data, 'quads_data_poor.csv'))

>>>>

dir_M <- c('Windows' = '//mazu.nceas.ucsb.edu/data_edit',
           'Darwin'  = '/Volumes/ohi',
           'Linux'   = '/home/shares/ohi')[[ Sys.info()[['sysname']] ]]

@@

loiczid_raster_file  <- file.path(dir_git, 'data/rasters/loiczid_raster.tif')
loiczid_raster       <- raster::raster(loiczid_raster_file)
names(loiczid_raster) <- 'loiczid'

@@

  ### species info list - scinames, IUCN species ID, AM species ID, category etc
  spp_list_base <- read_csv(file.path(dir_data, 'spp_am_v_iucn.csv'))
  create_spp_list2(spp_list_base, data_file, am_spp_cells, iucn_spp_cells, loiczid_raster)

}

@@

### attach group name text field, and occurcells field
spp_list <- spp_list %>%
  left_join(x <- read_csv(file.path(dir_data, 'sciname_lookups/spp_groupnames.csv')),
            by = 'spp_group') %>%
  left_join(read_csv(file.path(dir_data_remote, 'aquamaps/d2015/csv/speciesoccursum.csv')) %>% 
              select(am_sid = speciesid, occurcells),
            by = 'am_sid')

# cat_score_df <- data.frame(popn_category  = c('LC', 'NT', 'VU', 'EN', 'CR', 'EX', 'DD', 'NE'),
#                            category_score = c( 0.0,  0.2,  0.4,  0.6,  0.8,  1.0,   NA,  NA))
# spp_list <- spp_list %>%
#   left_join(cat_score_df, by = 'popn_category')

@@

``` {r counts_spp_all_observations, echo = FALSE}

spp_all <- read_csv(file.path(dir_data, 'spp_all.csv'))

@@

@@
